Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-09-18 main.tex
Typo, commit for the day

In addition, we note that the distribution of noise in \eqref{eqn:modified_measurement} approaches a Gaussian when true ranges are sufficiently larger than measurement variance, as
\begin{equation}
    \begin{split}
        &r_i << h_i(\rvec{x}_k) \\
        \implies &2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 - r_i \approx 2h_i(\rvec{x}_k)\rv{v}_{k,i} \\
        \implies &\rv{v}'_{k,i} \approx 2h_i(\rvec{x}_k)\rv{v}_{k,i}\,,
    \end{split} \label{eqn:modified_noise_approaches_gaussian}
\end{equation}
and conclude with the following assumption.
\begin{assum}
    Given property \eqref{eqn:modified_noise_approaches_gaussian}, and our $95\%$ confindence in the conservativness of variance estimates \eqref{eqn:modified_meaasurement_variance_estimate}, we assume that range measurements $\rv{z}_i$ are in general large enough to produce sufficiently Gaussian modified measurement noise $\rv{v}'_{k,i}$ and its variance estimated sufficiently conservative to be used in the EIF and measurement model \eqref{eqn:modified_measurement_model}.
\end{assum}

>>>>

In addition, we note that the distribution of noise in \eqref{eqn:modified_measurement} approaches a Gaussian when true ranges are sufficiently larger than measurement variances, as shown by
\begin{equation}
    \begin{split}
        &r_i << h_i(\rvec{x}_k) \\
        \implies &2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 - r_i \approx 2h_i(\rvec{x}_k)\rv{v}_{k,i} \\
        \implies &\rv{v}'_{k,i} \approx 2h_i(\rvec{x}_k)\rv{v}_{k,i}\,,
    \end{split} \label{eqn:modified_noise_approaches_gaussian}
\end{equation}
and conclude with the following assumption.
\begin{assum}
    Given property \eqref{eqn:modified_noise_approaches_gaussian}, and our $95\%$ confindence in the conservativness of variance estimates \eqref{eqn:modified_meaasurement_variance_estimate}, we assume that range measurements $\rv{z}_i$ are in general large enough to produce sufficiently Gaussian modified measurement noise $\rv{v}'_{k,i}$ and its variance estimated sufficiently conservative to be used in the EIF and measurement model \eqref{eqn:modified_measurement_model}.
\end{assum}
